---
title: "DNAComb QC"
output:
  html_document:
    number_sections: true
    toc: true
params:
  root_paths: !r character()
  library_files: !r character()
  record_counts_file: null
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
header-includes:
 \usepackage{float}
---

```{css, echo=FALSE}
/* ===== Layout ===== */

body {
  max-width: 1500px;
  margin-left: auto;
  margin-right: auto;
  padding-left: 260px;
  padding-right: 2rem;

  font-family: -apple-system, BlinkMacSystemFont, "Segoe UI",
               Roboto, Helvetica, Arial, sans-serif;

  font-size: 15px;
  line-height: 1.65;

  color: #2b2b2b;
  background-color: #fcfcfc;
}

html {
  scroll-behavior: smooth;
}

/* ===== Floating TOC ===== */

#TOC {
  position: fixed;
  left: 0;
  top: 0;

  width: 220px;
  height: 100%;

  overflow-y: auto;

  padding: 1.5rem 1rem;

  background: #f5f5f5;
  border-right: 1px solid #dddddd;

  font-size: 0.92em;
}

/* Remove bullets */
#TOC ul {
  list-style-type: none;
  padding-left: 0.6rem;
}

/* Reduce nested indent */
#TOC ul ul {
  padding-left: 1rem;
}

/* TOC links */
#TOC a {
  color: #444;
  text-decoration: none;
}

#TOC a:hover {
  color: #1f78b4;
  font-weight: 500;
}

#TOC li {
  margin-bottom: 0.35rem;
  line-height: 1.3;
}

/* ===== Headings ===== */

h1, h2, h3, h4 {
  color: #1f2937;
  font-weight: 600;
  margin-top: 2rem;
}

h1 {
  border-bottom: 2px solid #d9d9d9;
  padding-bottom: 0.3rem;
}

h2 {
  border-bottom: 1px solid #e5e5e5;
  padding-bottom: 0.2rem;
}

/* ===== Code ===== */

code {
  background: #f0f0f0;
  padding: 0.1em 0.3em;
  border-radius: 4px;
  font-size: 0.92em;
}

pre {
  background: #f7f7f7;
  border: 1px solid #e0e0e0;
  border-radius: 6px;
  padding: 0.8rem;
}

/* ===== Tables ===== */

table {
  border-collapse: collapse;
  width: 100%;
  margin-bottom: 1.5rem;
}

th {
  background: #f2f2f2;
  font-weight: 600;
}

th, td {
  padding: 0.5rem 0.75rem;
  border: 1px solid #dddddd;
}

p, ul, ol {
  margin-bottom: 1rem;
}

/* ===== Figures ===== */

img {
  max-width: 100%;
  border-radius: 4px;
}

.figure {
  margin-top: 1.5rem;
  margin-bottom: 1.5rem;
}

/* ===== Captions ===== */

.caption,
figcaption {
  color: #666;
  font-size: 0.92em;
  text-align: center;
  margin-top: 0.5rem;
}

/* ===== Small screens ===== */

@media screen and (max-width: 1000px) {

  #TOC {
    position: static;
    width: auto;
    height: auto;
    border-right: none;
    border-bottom: 1px solid #dddddd;
  }

  body {
    margin-left: auto;
    padding: 1rem;
  }
}
```

```{r setup, include=FALSE}
# Set parameters
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.pos = 'H', fig.align = "center")

library(magrittr)
library(tidyverse)
library(ggpubr)
library(ggtext)
library(patchwork)
library(kableExtra)

theme_set(theme_pubclean() + theme(legend.position = 'right',
                                   plot.title = element_text(hjust = 0.5),
                                   plot.subtitle = element_text(hjust = 0.5),
                                   strip.background = element_blank(),
                                   legend.key = element_blank()))

# Generate plot size based on number of samples
plot_size <- function(n, min = 4, per_sample = 0.25, max = 11, plus = 0) {
  max(min, min(max, per_sample * n + plus))
}

# Shorten long sample names
shorten_names <- function(x, max = 12) {
  make.unique(str_c(str_sub(x, end = max - 3), if_else(nchar(x) > max - 3, "...", "")), sep = "")
}

# Wrap long sequences
wrap_seq <- function(x, max_len=30, sep="<br>") {
  pat <- str_c("(.{", max_len, "})")
  rep <- str_c("\\1", sep)
  str_replace_all(x, pat, rep)
}

filter_colours <- c(
  unfiltered = "#4daf4a", empty_read = "#e41a1c", short_read = "#ff7f00",
  long_read = "#a65628", bad_alignment = "#984ea3", low_mean_quality = "#377eb8"
)

category_colours <- c(
  "match" = "green", "exact_match" = "green", "nearest_match" = "darkgreen",
  "mismatch" = "orange", "nonmatch" = "red",
  "recombination" = "blue", "exact_recombination" = "blue", "nearest_recombination" = "darkblue",
  "multimatch" = "purple", "uncompared" = "grey"
)
```

```{r data_import, include=FALSE}
read_lib <- function(x) {
  tbl <- read_tsv(x)
  name <- str_remove(basename(x), "\\..*$")
  if (!"_id" %in% names(tbl)) {
    tbl <- mutate(tbl, `_id` = str_c(name, 1:n()))
  }
  tbl
}

libraries <- map(params$library_files, read_lib) %>%
  set_names(str_remove(basename(params$library_files), "\\..*$"))

root_names <- basename(params$root_paths)

library_counts <- str_c(params$root_paths, ".library_counts.tsv") %>%
  set_names(root_names) %>%
  map(read_tsv) %>%
  bind_rows(.id = "_sample") %>%
  mutate(combination_status = factor(combination_status, levels = rev(names(category_colours))))

summary <- str_c(params$root_paths, ".summary.tsv") %>%
  set_names(root_names) %>%
  map(read_tsv) %>%
  bind_rows(.id = "_sample")

filtering <- str_c(params$root_paths, ".filtered.tsv") %>%
  set_names(root_names) %>%
  map(read_tsv) %>%
  bind_rows(.id = "_sample")

record_counts <- read_tsv(params$record_counts_file) %>%
  group_by(sample_id, stage, label, read) %>%
  summarise(records = sum(records), .groups = "drop") %>%
  pivot_wider(names_from = read, values_from = records)

regions <- setdiff(names(library_counts), c("_sample", "_sample_disp", "group", "combination_status",
                                            "combinations_in_library", "combination_id", "count"))
lib_regions <- map(libraries, ~regions[regions %in% names(.)])

samples <- sort(unique(c(
  library_counts$`_sample`, summary$`_sample`, filtering$`_sample`, record_counts$sample_id
)))
n_samples <- length(samples)
display_samples <- structure(shorten_names(samples), names = samples)

library_counts <- mutate(library_counts, `_sample_disp` = display_samples[`_sample`])
summary <- mutate(summary, `_sample_disp` = display_samples[`_sample`])
filtering <- mutate(filtering, `_sample_disp` = display_samples[`_sample`])
record_counts <- mutate(record_counts, `sample_id_disp` = display_samples[`sample_id`])

pairs_match <- case_when(
  "R2" %in% names(record_counts) && all(record_counts$R1 == record_counts$R2) ~ "paired_matching",
  "R2" %in% names(record_counts) && !all(record_counts$R1 == record_counts$R2) ~ "paired_unmatched",
  TRUE ~ "single_end"
)
```

This report summarises DNAComb output on the following `r n_samples` samples:

`r str_c(map2(names(display_samples), display_samples, \(x, y) if (x == y) str_c("* ", x) else str_c("* ", x, " (", y, ")")), collapse = "\n")`

Shortened names (in brackets) are used in figures where the originals are too long to display cleanly.  

Comparison was run against expected sequences in these libraries containing the bracketed regions:

`r str_c(map2(names(lib_regions), lib_regions, \(x, y) str_c("* ",x, " (", str_c(y, collapse = ", "), ")")), collapse = "\n")`  
  
The final counts output by DNAComb are as follows:
```{r summary_table}
filter(summary, group == "all", metric == "total") %>% select(Sample = `_sample_disp`, Total = count) %>%
  left_join(filter(summary, group == "unfiltered", metric == "total") %>% select(Sample = `_sample_disp`, Unfiltered = count),
            by = join_by(Sample)) %>%
  left_join(filter(summary, group == "unfiltered", metric %in% c("exact_match", "nearest_match")) %>% 
              count(`_sample_disp`, wt = count) %>%
              select(Sample = `_sample_disp`, Assigned = n),
            by = join_by(Sample)) %>%
  mutate(`% Unfiltered` = scales::percent(Unfiltered / Total, accuracy = 0.1),
         `% Assigned` = scales::percent(Assigned / Total, accuracy = 0.1)) %>%
  select(Sample, Total, Unfiltered, `% Unfiltered`, Assigned, `% Assigned`) %>%
  knitr::kable()
```

# Pipeline

The pipeline started from raw `r if(pairs_match == "single_end"){"single"} else {"paired"}` end reads and applied the following operations:
```{r pipeline}
ops <- distinct(record_counts, label) %>%
  filter(label %in% c("downsampled", "merged", "trimmed")) %>%
  pull(label)

out <- c("downsampled", "merged", "trimmed")
out <- out[out %in% ops]
out <- c(downsampled = "Downsampling (SeqTK)", merged = "Read Merging (PEAR)", trimmed = "Read Trimming (CutAdapt)")[out]
out <- str_c("* ", c(out, "Counting (DNAComb)"), collapse = "\n")
```
`r out`

`r if(pairs_match == "paired_unmatched") "WARNING: Forward and reverse read counts differ at at least 1 stage:"`
`r if(pairs_match == "paired_unmatched") knitr::kable(record_counts)`
`r if(pairs_match == "paired_unmatched") "This indicates a serious error somewhere during processing"`

```{r pipeline_fig, fig.height=plot_size(n_samples, plus = 2, per_sample = 1.5, max = Inf), fig.width=7, fig.cap="Reads retained at each pipeline stage"}
stage_colours <- c(
  header1 = "white", raw = "#377eb8", gap1 = "white", gap2 = "white",
  header2 = "white", downsampled = "#377eb8", gap3 = "white", gap4 = "white",
  header3 = "white", merged = "#377eb8", unmerged = "#ff7f00", discarded = "#e41a1c",
  header4 = "white", trimmed = "#377eb8", untrimmed = "#e41a1c", gap5 = "white",
  header5 = "white", assigned = "#377eb8", unassigned = "#ff7f00", filtered = "#e41a1c"
)

stage_col_labs <- c(
  header1 = "**Raw Reads**", raw = "Reads",  gap1 = "", gap2 = "",
  header2 = "**Downsampling**", downsampled = "Downsampled", gap3 = "", gap4 = "",
  header3 = "**Merging**", merged = "Merged", unmerged = "Unmerged", discarded = "Discarded",
  header4 = "**Trimming**", trimmed = "Trimmed", untrimmed = "Untrimmed", gap5 = "",
  header5 = "**Counting**", assigned = "Assigned", unassigned = "Unassigned", filtered = "Filtered"
)

pipeline_counts <- bind_rows(
  record_counts,
  select(summary, `_sample_disp`, group, metric, count) %>%
    filter(group == "filtered" & metric == "total" | group != "filtered" & metric != "total") %>%
    mutate(
      label = case_when(
        group == "filtered" ~ "filtered",
        metric %in% c("exact_match", "nearest_match") ~ "assigned",
        TRUE ~ "unassigned"
      ),
      stage = max(record_counts$stage) + 1
    ) %>%
    count(sample_id_disp = `_sample_disp`, stage, label, wt = count, name = "R1")
) %>%
  group_by(stage) %>%
  mutate(stage_name = case_when(
    "raw" %in% label ~ "Raw",
    "downsampled" %in% label ~ "Downsampling",
    "merged" %in% label ~ "Merging",
    "trimmed" %in% label ~ "Trimming",
    "assigned" %in% label ~ "Counting",
    TRUE ~ str_c("Stage ", stage)
  )) %>%
  ungroup() %>%
  arrange(stage) %>%
  mutate(stage_name = factor(stage_name, levels = unique(stage_name)),
         label = factor(label, levels = names(stage_colours)))

ggplot(pipeline_counts, aes(x = stage_name, y = R1, fill = label)) +
  facet_grid(rows = vars(sample_id_disp), labeller = label_wrap_gen()) +
  geom_col(position = position_stack(), show.legend = TRUE) +
  scale_fill_manual(name = "", values = stage_colours, drop = FALSE,
                    limits = names(stage_colours), labels = stage_col_labs) +
  guides(fill = guide_legend(nrow = 4)) +
  labs(x = "", y = "Count") +
  theme(strip.placement = "outside",
        legend.text = element_markdown(),
        legend.position = "bottom")
```

```{r pipeline_loss, fig.cap="Fraction of reads retained after each stage"}
pipeline_counts %>%
  filter(label %in% c("raw", "downsampled", "merged", "trimmed", "assigned")) %>% 
  arrange(stage) %>%
  select(sample_id_disp, label, R1) %>%
  pivot_wider(names_from = label, values_from = R1) %>%
  mutate(across(-sample_id_disp, ~scales::label_percent(accuracy = 0.1)(./raw))) %>%
  knitr::kable(digits = 4)
```

# DNAComb Filtering

```{r filtering_fig, fig.height=plot_size(n_samples), fig.width=7, fig.cap="Reads filtered by DNAComb"}
p_filtering_abs <- filter(summary, group == "filtered" & metric != "total" | group == "unfiltered" & metric == "total") %>%
  mutate(metric = if_else(group == "filtered", metric, "unfiltered"),
         metric = factor(metric, levels = rev(names(filter_colours)))) %>%
  ggplot(aes(x = `_sample_disp`, y = count, fill = metric)) +
  geom_col(width = 0.5) +
  scale_fill_manual(name = "", values = filter_colours) +
  labs(x = "", y = "Reads") +
  coord_flip() +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
        axis.ticks.y = element_blank(),
        legend.position = "bottom")

p_filtering_prop <- filter(summary, group == "filtered" & metric != "total" | group == "unfiltered" & metric == "total") %>%
  mutate(metric = if_else(group == "filtered", metric, "unfiltered"),
         metric = factor(metric, levels = rev(names(filter_colours)))) %>%
  ggplot(aes(x = `_sample_disp`, y = overall_proportion, fill = metric)) +
  geom_col(width = 0.5) +
  scale_fill_manual(name = "", values = filter_colours) +
  labs(x = "", y = "Proportion of reads") +
  coord_flip() +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
        axis.ticks.y = element_blank(),
        legend.position = "bottom")

p_filtering_abs + p_filtering_prop + guide_area() +
  plot_layout(heights = c(1, 0.2), widths = c(0.5, 0.5), design = "12\n33", guides = "collect")
```

`r if (nrow(filtering) > 0) "The most common filtered reads were:"`
`r if (nrow(filtering) == 0) "No reads were filtered."`

```{r filtering_table}
if (nrow(filtering) > 0) {
  arrange(filtering, desc(count)) %>%
    slice_head(n = 5) %>%
    rename(sample = `_sample`) %>%
    select(-`_sample_disp`) %>%
    mutate(across(c(forward, reverse), \(x) wrap_seq(x, 35, "\n"))) %>%
    kbl(digits = 4, format = "html") %>%
    kable_styling() %>%
    column_spec(3:4, width_max = "10cm") %>%
    scroll_box(width = "100%", height = "500px")
}
```

# DNAComb Assignment

```{r assignment_fig, fig.height=plot_size(n_samples), fig.width=7, fig.cap="DNAComb read assignment"}
p_matches_abs <- filter(summary, group == "unfiltered", metric != "total") %>%
  mutate(metric = factor(metric, levels = rev(names(category_colours)))) %>%
  ggplot(aes(x = `_sample_disp`, y = count, fill = metric)) +
  geom_col(width = 0.5) +
  scale_fill_manual(name = "", values = category_colours) +
  labs(x = "", y = "Reads") +
  coord_flip() +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
        axis.ticks.y = element_blank(),
        legend.position = "bottom")

p_matches_prop <- filter(summary, group == "unfiltered", metric != "total") %>%
  mutate(metric = factor(metric, levels = rev(names(category_colours)))) %>%
  ggplot(aes(x = `_sample_disp`, y = group_proportion, fill = metric)) +
  geom_col(width = 0.5) +
  scale_fill_manual(name = "", values = category_colours) +
  labs(x = "", y = "Proportion of reads") +
  coord_flip() +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
        axis.ticks.y = element_blank(),
        legend.position = "bottom")

p_matches_abs + p_matches_prop + guide_area() +
  plot_layout(heights = c(1, 0.2), widths = c(0.5, 0.5), design = "12\n33", guides = "collect")
```

# Library Completeness

```{r completeness_fig, fig.height=plot_size(n_samples, plus = 0), fig.width=7, fig.cap="Fraction of combinations observed in each library"}
calc_count <- function(regs, expected) {
  filter(library_counts, combination_status == "match", combinations_in_library == 1) %>%
    select(`_sample_disp`, group, !!!rlang::syms(regs)) %>%
    distinct(`_sample_disp`, !!!rlang::syms(regs)) %>%
    group_by(`_sample_disp`) %>%
    summarise(observed = n(), expected = expected)
}

if (length(libraries) > 1) {
  completeness <- bind_rows(
    map2(lib_regions, map_dbl(libraries, nrow), calc_count) %>% bind_rows(.id = "library"),
    calc_count(unname(unlist(lib_regions)), reduce(libraries, \(i, x) i * nrow(x), .init = 1)) %>% mutate(library = "Combination")
  ) %>%
    mutate(p = observed / expected, library = factor(library, levels = c(sort(unique(library[library != "Combination"])), "Combination")))

  ggplot(completeness, aes(y = `_sample_disp`, x = p, fill = library)) +
    geom_col(width = 0.5, position = position_dodge()) +
    lims(x = c(0, 1)) +
    labs(x = "Completeness", y = "") +
    scale_fill_brewer(name = "Library", palette = "Set1") +
    theme(panel.grid.major.y = element_blank(),
          panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
          axis.ticks.y = element_blank())
} else {
  completeness <- calc_count(lib_regions[[1]], nrow(libraries[[1]])) %>%
    mutate(p = observed / expected)
  
  ggplot(completeness, aes(y = `_sample_disp`, x = p)) +
    geom_col(width = 0.5, fill = "#377eb8", position = position_dodge()) +
    lims(x = c(0, 1)) +
    labs(x = "Completeness", y = "") +
    theme(panel.grid.major.y = element_blank(),
          panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
          axis.ticks.y = element_blank())
}
```

# Library Representation
```{r representation_fig, fig.height=6, fig.width=7, fig.cap="Library Representation"}
calc_library_representation <- function(tbl, ...) {
  if (nrow(tbl) == 0) {
    return(mutate(tbl, rank = numeric(), prop_reads = numeric(),
                  prop_rank = numeric(), cumprop_reads = numeric()))
  }

  group_by(tbl, ...) %>%
    arrange(count) %>%
    mutate(rank = 1:n(),
           prop_reads = count/sum(count),
           prop_rank = rank/max(rank),
           cumprop_reads = cumsum(prop_reads),
           auc = sum(diff(prop_rank) * (head(cumprop_reads,-1) + tail(cumprop_reads,-1)))/2) %>%
    ungroup()
}

rep_all <- count(library_counts, `_sample_disp`, !!!rlang::syms(regions), combination_status, combinations_in_library,
                 combination_id, wt = count, name = "count") %>%
  calc_library_representation(`_sample_disp`)

rep_lib <- filter(library_counts, combinations_in_library == 1) %>%
  count(`_sample_disp`, !!!rlang::syms(regions), combination_status, combinations_in_library,
        combination_id, wt = count, name = "count") %>%
  calc_library_representation(`_sample_disp`)

if (n_samples > 8) {
  top_lib <- distinct(rep_all, `_sample_disp`, auc) %>%
    arrange(auc) %>%
    slice(c(1, 2, 3, 4, n() - 3, n() - 2, n() - 1, n())) %>%
    pull(`_sample_disp`)

  p_rep_all <- ggplot(mapping = aes(x = prop_rank, y = cumprop_reads)) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    geom_line(data = filter(rep_all, !`_sample_disp` %in% top_lib), mapping = aes(group = `_sample_disp`)) +
    geom_line(data = filter(rep_all, `_sample_disp` %in% top_lib), mapping = aes(colour = `_sample_disp`)) +
    labs(x = "Proportional Rank", y = "Cumulative Proportion of Reads", title = "All Combinations") +
    scale_colour_brewer(palette = "Dark2", name = "") +
    guides(colour = guide_legend(direction = "horizontal", nrow = 3))

  p_rep_lib <- ggplot(mapping = aes(x = prop_rank, y = cumprop_reads)) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    geom_line(data = filter(rep_lib, !`_sample_disp` %in% top_lib), mapping = aes(group = `_sample_disp`)) +
    geom_line(data = filter(rep_lib, `_sample_disp` %in% top_lib), mapping = aes(colour = `_sample_disp`)) +
    labs(x = "Proportional Rank", y = "Cumulative Proportion of Reads", title = "In Library") +
    scale_colour_brewer(palette = "Dark2", name = "") +
    guides(colour = guide_legend(direction = "horizontal", nrow = 3))
} else {
  leg_rows <- case_when(
    n_samples > 6 ~ 3,
    n_samples > 3 ~ 2,
    TRUE ~ 1
  )

  p_rep_all <- ggplot(rep_all, aes(x = prop_rank, y = cumprop_reads, colour = `_sample_disp`)) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    geom_line() +
    labs(x = "Proportional Rank", y = "Cumulative Proportion of Reads", title = "All Combinations") +
    scale_colour_brewer(palette = "Dark2", name = "") +
    guides(colour = guide_legend(direction = "horizontal", nrow = leg_rows))

  p_rep_lib <- ggplot(rep_lib, aes(x = prop_rank, y = cumprop_reads, colour = `_sample_disp`)) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    geom_line() +
    labs(x = "Proportional Rank", y = "Cumulative Proportion of Reads", title = "In Library") +
    scale_colour_brewer(palette = "Dark2", name = "") +
    guides(colour = guide_legend(direction = "horizontal", nrow = leg_rows))
}

p_rep_all + p_rep_lib + guide_area() +
  plot_layout(heights = c(1, 0.2), widths = c(0.5, 0.5), design = "12\n33", guides = "collect", axis_titles = "collect")
```

```{r lib_representation_fig, fig.height=plot_size(length(libraries) %/% 2, min = 6, plus = 2, per_sample = 4), fig.width=7, fig.cap="Sub-library Representation"}
calc_rep_lib <- function(lib, regs) {
  count(library_counts, `_sample_disp`, !!!rlang::syms(regs), wt = count, name = "count") %>%
    full_join(lib) %>%
    drop_na(!!!rlang::syms(regs)) %>%
    complete(`_sample_disp`, nesting(!!!rlang::syms(regs), `_id`), fill = list(count = 0)) %>%
    calc_library_representation(`_sample_disp`) %>%
    select(`_sample_disp`, count:auc)
}

if (length(libraries) > 1) {
  representation <- map2(libraries, lib_regions, calc_rep_lib) %>%
    bind_rows(.id = "library")
  
  if (n_samples > 8) {
    top_lib <- distinct(representation, `_sample_disp`, auc) %>%
      arrange(auc) %>%
      slice(c(1, 2, 3, 4, n() - 3, n() - 2, n() - 1, n())) %>%
      pull(`_sample_disp`)
    
    ggplot(mapping = aes(x = prop_rank, y = cumprop_reads)) +
      facet_wrap(~library, ncol = 2) +
      geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
      geom_line(data = filter(representation, !`_sample_disp` %in% top_lib), mapping = aes(group = `_sample_disp`)) +
      geom_line(data = filter(representation, `_sample_disp` %in% top_lib), mapping = aes(colour = `_sample_disp`)) +
      labs(x = "Proportional Rank", y = "Cumulative Proportion of Reads") +
      scale_colour_brewer(palette = "Dark2", name = "") +
      guides(colour = guide_legend(direction = "horizontal", nrow = 2)) +
      theme(legend.position = "bottom")
  } else {
    leg_rows <- case_when(
      n_samples > 6 ~ 2,
      TRUE ~ 1
    )
    
    ggplot(representation, aes(x = prop_rank, y = cumprop_reads, colour = `_sample_disp`)) +
      facet_wrap(~library, ncol = 2) +
      geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
      geom_line() +
      labs(x = "Proportional Rank", y = "Cumulative Proportion of Reads") +
      scale_colour_brewer(palette = "Dark2", name = "") +
      guides(colour = guide_legend(direction = "horizontal", nrow = leg_rows)) +
      theme(legend.position = "bottom")
  }
}
```
